Estimating Output Loss due to being Unrecognized as States

### 2019-03-05 paper/paper.tex
Revise the methodology #1 #50
Instead of predicting real GDP in levels, we now predict real GDP growth, to avoid estimating country fixed effects

\subsection{Country boundaries}
To aggregate nighttime light intensity at the 30 arc-second cell level into the country level, we need the spatial data on country boundaries. 
We use GADM (2018), following Alesina et al.\ (2016) and Dreher et al.\ (2015) among others. 
The data include 256 countries and overseas territories. 
One country, Vatican, is dropped from the sample because it is smaller than the 30 arc-second cell. 
In addition, 75 countries and territories are also dropped from the sample as real GDP data is unavailable for all years from 1992 to 2013.
Excluding the three parent states of unrecognized states (Georgia, Azerbaijan, and Moldova), our base sample thus consists of 177 countries/territories in total.
\section{Methodology}
% Model of real GDP
We model real GDP in territory $i$ in year $t$, denoted by $y_{it}$, as follows:
\begin{equation}\label{gdp}
\ln(y_{it}) = \beta \ln(L_{it}) + \mu_i + \eta_t + \varepsilon_{it},
\end{equation}
where $L_{it}$ is nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{it}$ the error term.

@@

% Model of country fixed effects
To predict $y_{it}$ for unrecognized states (and their parent countries dropped from the sample) from equation (\ref{gdp}), we need to recover territory fixed effects, $\mu_i$. 
We predict them with the average light intensity over the sample period of 1992-2013. 
Specifically, with the same set of countries as the one for estimating equation (\ref{gdp}), we estimate the following equation with OLS:
\begin{equation}\label{country_fe}
\hat{\mu}_i = \alpha + \gamma \ln(\bar{L}_{i}) + \xi_{i},
\end{equation}
where $\hat{\mu}_i$ is the estimated territory fixed effect from equation (\ref{gdp}), $\bar{L}_{i}$ the average light intensity in territory $i$ over the sample period, and $\xi_i$ the error term.

% Prediction of real GDP
Consequently, GDP per capita in unrecognized state $k$ in year $t$, denoted by $\hat{y}_{kt}$, will then be predicted as follows:
\begin{equation}\label{prediction}
\ln(\hat{y}_{kt}) = \hat{\beta} \ln(L_{kt}) + [\hat{\alpha} + \hat{\gamma} \ln(\bar{L}_{i})]  + \hat{\eta_t},
\end{equation}
where $\hat{\beta}$ and $\hat{\eta_t}$ are the estimated $\beta$ and $\eta_t$ in equation (\ref{gdp}), $\hat{\alpha}$ and $\hat{\gamma}$ the estimated $\alpha$ and $\gamma$ in equation (\ref{country_fe}).

>>>>

\subsection{Country boundaries}
To aggregate nighttime light intensity at the 30 arc-second cell level into the country level, we need the spatial data on country boundaries. 
We use GADM (2018), following Alesina et al.\ (2016) and Dreher et al.\ (2015) among others. 
The data include 256 countries and overseas territories. 
One country, Vatican, is dropped from the sample because it is smaller than the 30 arc-second cell. 
In addition, 75 countries and territories are also dropped from the sample as real GDP data is unavailable for all years from 1992 to 2013.
Excluding the three parent states of unrecognized states (Georgia, Azerbaijan, and Moldova), our base sample thus consists of 177 countries/territories in total.
\section{Methodology}
% Model of real GDP
Following Henderson et al.\ (2012), we model real GDP in territory $i$ in year $t$, denoted by $y_{i,t}$, as follows:
\begin{equation}\label{gdp}
\ln y_{i,t} = \beta \ln L_{i,t} + \mu_i + \eta_t + \varepsilon_{i,t},
\end{equation}
where $L_{i,t}$ is nighttime light intensity in territory $i$ in year $t$, $\mu_i$ the territory fixed effect, $\eta_t$ the year fixed effect, and $\varepsilon_{i,t}$ the error term.

@@

% Predict real GDP growth for unrecognized states
For unrecognized state $i$, we cannot predict $y_{i,t}$ from equation (\ref{gdp}) because there is no straightforward way to estimate $\mu_i$. However, we can predict the annual growth rate of $y_{i,t}$, denoted by $\hat{g}_{i,t}$, by taking the first-difference of equation (\ref{gdp}) to remove $\mu_i$:
\begin{eqnarray}\label{growth}
\hat{g}_{i,t} 
&=& \ln \hat{y}_{i,t} - \ln \hat{y}_{i, t-1} \nonumber \\
&=& \hat{\beta} (\ln L_{i,t} - \ln L_{i,t-1}) + (\hat{\eta}_t - \hat{\eta}_{t-1}),
\end{eqnarray}
where $\hat{\beta}$ and $\hat{\eta_t}$ are the estimated $\beta$ and $\eta_t$ in equation (\ref{gdp}).
